---
title: "LinearModel"
author: "Taylor Dickie-Mahtesian"
date: "10/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)
require(tidyverse)
require(tigerstats)
```

# Introduction

Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

## SIMS~ARM Regression

```{r}
plot(SIMS~ARM,data=data)
```

This scatter plot looks like a linear trend going uphill to the right which is a sign of positively correlated set of data.

The greater the arm strength(ARM) mean the greater the simulator rating(SIMS) will be.

```{r}
cor(SIMS~ARM,data=data)
```
The Number above is the coordination between SIMS and ARM. Correlation is a measure of the linear association of two variables.  

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The equations is SIMS= -4.095160 + 0.054563 * ARM

```{r}
newData=data.frame(GRIP=94, ARM=88)
predict.lm(model.1,newData, interval = "prediction")
```


## SIMS~GRIP Regression


```{r}
plot(SIMS~GRIP,data=data)
```



## SIMS~Arm+GRIP Regression


## MODEL COMPARISONS